1000 Graphs

### 2021-06-28 graphs_newt_snakes/fig_1000.Rmd
updated the r figures for the 1000 gen simulation. There is osmthing oof about the difference graph (like the lines might not be connected to each other). goal is to think of better ways to do it

```{r pressure, echo=FALSE}
newt_max_pheno = 0
snake_max_pheno = 0

@@

  if (max(file$Newt_max_Pheno) > newt_max_pheno){
    newt_max_pheno = max(file$Newt_max_Pheno) }

  if (max(file$Snake_max_Pheno) > snake_max_pheno){
    snake_max_pheno = max(file$Snake_max_Pheno) }
}
  print(newt_max_pheno)
  print(snake_max_pheno)
```
## The Figure
Loop through the files and find the max and min of each of the species pheotypes
Then set up a graph with the max max
Loop though the files and make two lines (red for newts blue for snakes) and keep a minimum about of info in mem at a time

This is the correct one
```{r pressure, echo=FALSE}
newt_max_pheno = 0
snake_max_pheno = 0

@@

  file <- read.table(current_file, header = TRUE)
  #print(max(file$Newt_max_Pheno))
  #print(max(file$Snake_max_Pheno))
  if (max(file$Newt_max_Pheno) > newt_max_pheno){
    newt_max_pheno = max(file$Newt_max_Pheno) }

  if (max(file$Snake_max_Pheno) > snake_max_pheno){
    snake_max_pheno = max(file$Snake_max_Pheno) }
}

  print(newt_max_pheno)
  print(snake_max_pheno)
```
## The Figure
Loop through the files and find the max and min of each of the species pheotypes
Then set up a graph with the max max
Loop though the files and make two lines (red for newts blue for snakes) and keep a minimum about of info in mem at a time

@@

```{r pressure, echo=FALSE}
newt_max_pheno = 0
snake_max_pheno = 0

@@

for (current_file in files){
  print(current_file)

  file <- read.table(current_file, header = TRUE)
  file$Newt_max_Pheno[file$Newt_max_Pheno == "NULL"] <- NA
  file$Snake_max_Pheno[file$Snake_max_Pheno == "NULL"] <- NA
  print(max(file$Newt_max_Pheno, na.rm = TRUE))
  print(max(file$Snake_max_Pheno, na.rm = TRUE))
  if (max(file$Newt_max_Pheno, na.rm = TRUE) > newt_max_pheno){
    newt_max_pheno = max(file$Newt_max_Pheno, na.rm = TRUE) }

  if (max(file$Snake_max_Pheno, na.rm = TRUE) > snake_max_pheno){
    snake_max_pheno = max(file$Snake_max_Pheno, na.rm = TRUE) }
}

  print(newt_max_pheno)
  print(snake_max_pheno)
```
some of these values are in quotes, why?

Some other things that might be goo to look at:
The average of the phenotypes
The difference between the average phenotypes

```{r pressure, echo=FALSE}
ggplot()+
  geom_line(current_file, aes(gen, snake), color="blue")+
  geom_line(current_file, aes(gen, snake), color="red")+
  geom_point(size=3, color = "darkgreen")+
  ggtitle("How the Phenotypes Change Through the Generations") + 
  xlab("Generation") + 
  ylab("Phenotype Level") +
  theme_bw()
```

>>>>

```{r data from the mistake folder, echo=FALSE}
newt_max_pheno_1 = 0
snake_max_pheno_1 = 0
newt_min_pheno_1 = 0
snake_min_pheno_1 = 0
true_max_1 = 0
true_min_1 = 0
min_difference_1 = 0
max_difference_1 = 0

@@

  file$Newt_max_Pheno[file$Newt_max_Pheno == "NULL"] <- NA
  file$Snake_max_Pheno[file$Snake_max_Pheno == "NULL"] <- NA
  file$Newt_min_Pheno[file$Newt_min_Pheno == "NULL"] <- NA
  file$Snake_min_Pheno[file$Snake_min_Pheno == "NULL"] <- NA
  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA

  if (max(file$Newt_max_Pheno) > newt_max_pheno_1){
    newt_max_pheno_1 = max(file$Newt_max_Pheno) }

  if (max(file$Snake_max_Pheno) > snake_max_pheno_1){
    snake_max_pheno_1 = max(file$Snake_max_Pheno) }

  if (min(file$Newt_min_Pheno) < newt_min_pheno_1){
    newt_min_pheno_1 = min(file$Newt_min_Pheno) }

  if (min(file$Snake_min_Pheno) > snake_min_pheno_1){
    snake_min_pheno_1 = max(file$Snake_min_Pheno) }

  if (as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE)) < min_difference_1){
    min_difference_1 = as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE))
  }

  if (as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE)) > max_difference_1){
    max_difference_1 = as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE))
  }
}

  print(newt_max_pheno_1)
  print(snake_max_pheno_1)
   print(newt_min_pheno_1)
  print(snake_min_pheno_1)

  if (newt_max_pheno_1 > snake_max_pheno_1){
    true_max_1 = newt_max_pheno_1 }
  if ( snake_max_pheno_1 > newt_max_pheno_1){
    true_max_1 = snake_max_pheno_1 }

    if (newt_min_pheno_1 < snake_min_pheno_1){
    true_min_1 = newt_min_pheno_1 }
  if ( snake_min_pheno_1 < newt_min_pheno_1){
    true_min_1 = snake_min_pheno_1 }

```
```{r phenotype graph for mistake sims, echo=FALSE}

files <- list.files(path="~/Desktop/pheno_test_1000_old/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
file1 <- read.table(files[1], header = TRUE)
p <- ggplot(file1, aes(x=gen)) +
  xlim(0, 1000)+
  #ylim(0, true_max_1)+
  scale_y_log10(limits=c(true_min_1+0.8, true_max_1))+
  geom_line(aes(y = Newt_mean_Pheno), color = "darkred") + 
  geom_line(aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash")+
  ggtitle("Phenotype Measurements for Newts and Snakes") +
  xlab("Generation") + ylab("Average Phenotypes")+
  theme_bw()

  file <- read.table(current_file, header = TRUE)
 p <- p +
  geom_line(data=file, aes(y = Newt_mean_Pheno), color = "darkred") + 
  geom_line(data=file, aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash") 
  #Sys.sleep(2)

}

p 
```

```{r difference wrong sim, echo=FALSE}

## need to work on making this figure better 
files <- list.files(path="~/Desktop/pheno_test_1000_old/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
file1 <- read.table(files[1], header = TRUE)
p <- ggplot(file1, aes(x=gen)) +
  xlim(0, 1000)+
  #ylim(min_difference, max_difference)+
  #scale_y_continuous(trans=log10_trans(), limits=c(min_difference, max_difference))+
  #scale_y_log10()+
  scale_y_log10(limits=c(min_difference_1, max_difference_1))+
  geom_line(aes(y = Snake_mean_Pheno - Newt_mean_Pheno), color = "mediumseagreen") + 
    ggtitle("Difference Between Phenotypes (Snakes-Newts)") +
  xlab("Generation") + ylab("Average Difference")+
  theme_bw()

  file <- read.table(current_file, header = TRUE)
  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA
  file <- file[complete.cases(file), ]
  file$mean_dif = as.numeric(file$Snake_mean_Pheno) - as.numeric(file$Newt_mean_Pheno)
  file$mean_dif[file$mean_dif == 0] <- 0.01
  file$pos <- TRUE
  file$pos[file$mean_dif < 0] <- FALSE

 p <- p + geom_line(data=file, aes(x=gen, y=abs(mean_dif), color = pos), na.rm=TRUE)
  #Sys.sleep(2) na.rm=TRUE
 # color = "mediumseagreen"

}

p 
```

This is the correct one
```{r data 1 msprime photype graph, echo=FALSE}
newt_max_pheno_2 = 0
snake_max_pheno_2 = 0
newt_min_pheno_2 = 0
snake_min_pheno_2 = 0
true_max_2 = 0
true_min_2 = 0
min_difference_2 = 0
max_difference_2 = 0

@@

  file <- read.table(current_file, header = TRUE)
  #print(max(file$Newt_max_Pheno))
  #print(max(file$Snake_max_Pheno))

  file$Newt_max_Pheno[file$Newt_max_Pheno == "NULL"] <- NA
  file$Snake_max_Pheno[file$Snake_max_Pheno == "NULL"] <- NA
  file$Newt_min_Pheno[file$Newt_min_Pheno == "NULL"] <- NA
  file$Snake_min_Pheno[file$Snake_min_Pheno == "NULL"] <- NA
  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA

  if (max(file$Newt_max_Pheno) > newt_max_pheno_2){
    newt_max_pheno_2 = max(file$Newt_max_Pheno) }

  if (max(file$Snake_max_Pheno) > snake_max_pheno_2){
    snake_max_pheno_2 = max(file$Snake_max_Pheno) }

  if (min(file$Newt_min_Pheno) < newt_min_pheno_2){
    newt_min_pheno_2 = max(file$Newt_min_Pheno) }

  if (max(file$Snake_min_Pheno) < snake_min_pheno_2){
    snake_min_pheno_2 = max(file$Snake_min_Pheno) }

  if (as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE)) < min_difference_2){
      min_difference_2 = as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE))
  }

  if (as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE)) > max_difference_2){
    max_difference_2 = as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE))
  }
}

  print(newt_max_pheno_2)
  print(snake_max_pheno_2)
  print(newt_min_pheno_2)
  print(snake_min_pheno_2)

  if (newt_max_pheno_2 > snake_max_pheno_2){
    true_max_2 = newt_max_pheno_2 }
  if ( snake_max_pheno_2 > newt_max_pheno_2){
    true_max_2 = snake_max_pheno_2 }

  if (newt_min_pheno_2 < snake_min_pheno_2){
    true_min_2 = newt_min_pheno_2 }
  if ( snake_min_pheno_2 < newt_min_pheno_2){
    true_min_2 = snake_min_pheno_2 }
```

```{r data 1 msprime dif pheno graph, echo=FALSE}

files <- list.files(path="~/Desktop/pheno_test_1000/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
file1 <- read.table(files[1], header = TRUE)
p <- ggplot(file1, aes(x=gen)) +
  xlim(0, 1000)+
  #ylim(0, true_max_2)+
  scale_y_log10(limits=c(true_min_2+0.5, true_max_2))+
  geom_line(aes(y = Newt_mean_Pheno), color = "darkred") + 
  geom_line(aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash")+
  ggtitle("Phenotype Measurements for Newts and Snakes") +
  xlab("Generation") + ylab("Average Phenotypes")+
  theme_bw()

  file <- read.table(current_file, header = TRUE)
 p <- p +
  geom_line(data=file, aes(y = Newt_mean_Pheno), color = "darkred") + 
  geom_line(data=file, aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash") 
  #Sys.sleep(2)

}

p 
```
```{r data from multiple msprime, echo=FALSE}

files <- list.files(path="~/Desktop/pheno_test_1000/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
file1 <- read.table(files[1], header = TRUE)
p <- ggplot(file1, aes(x=gen)) +
  xlim(0, 1000)+
  #ylim(min_difference, max_difference)+
  #scale_y_continuous(trans=log10_trans(), limits=c(min_difference, max_difference))+
  #scale_y_log10()+
  scale_y_log10(limits=c(min_difference_2, max_difference_2))+
  geom_line(aes(y = Snake_mean_Pheno - Newt_mean_Pheno), color = "mediumseagreen") + 
    ggtitle("Difference Between Phenotypes (Snakes-Newts)") +
  xlab("Generation") + ylab("Average Difference")+
  theme_bw()

  file <- read.table(current_file, header = TRUE)
  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA
  file <- file[complete.cases(file), ]
  file$mean_dif = as.numeric(file$Snake_mean_Pheno) - as.numeric(file$Newt_mean_Pheno)
  file$mean_dif[file$mean_dif == 0] <- 0.01
  file$pos <- TRUE
  file$pos[file$mean_dif < 0] <- FALSE

 p <- p + geom_line(data=file, aes(x=gen, y=abs(mean_dif), color = pos), na.rm=TRUE)
  #Sys.sleep(2) na.rm=TRUE
 # color = "mediumseagreen"

}

p 
```

@@

```{r pressure, echo=FALSE}
newt_max_pheno_3 = 0
snake_max_pheno_3 = 0
newt_min_pheno_3 = 0
snake_min_pheno_3 = 0
true_max_3 = 0
true_min_3 = 0
max_difference_3 = 0
min_difference_3 = 0

@@

  file <- read.table(current_file, header = TRUE)
  file$Newt_max_Pheno[file$Newt_max_Pheno == "NULL"] <- NA
  file$Snake_max_Pheno[file$Snake_max_Pheno == "NULL"] <- NA
  file$Newt_min_Pheno[file$Newt_min_Pheno == "NULL"] <- NA
  file$Snake_min_Pheno[file$Snake_min_Pheno == "NULL"] <- NA
  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA
  #print(max(file$Newt_max_Pheno, na.rm = TRUE))
  #print(max(file$Snake_max_Pheno, na.rm = TRUE))

  if (as.numeric(max(file$Newt_max_Pheno, na.rm = TRUE)) > newt_max_pheno_3){
    newt_max_pheno_3 = as.numeric(max(file$Newt_max_Pheno, na.rm = TRUE)) }

  if (as.numeric(max(file$Snake_max_Pheno, na.rm = TRUE)) > snake_max_pheno_3){
    snake_max_pheno = as.numeric(max(file$Snake_max_Pheno, na.rm = TRUE)) }

  if (as.numeric(min(file$Newt_min_Pheno, na.rm = TRUE)) < newt_min_pheno_3){
    newt_min_pheno_3 = as.numeric(max(file$Newt_min_Pheno, na.rm = TRUE)) }

  if (as.numeric(max(file$Snake_min_Pheno, na.rm = TRUE)) < snake_min_pheno_3){
    snake_min_pheno_3 = as.numeric(max(file$Snake_min_Pheno, na.rm = TRUE)) }

 if (as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE)) < min_difference_3){
    min_difference_3 = as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE))
  }

  if (as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE)) > max_difference_3){
    max_difference_3 = as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE))
  }

      }

  print(newt_max_pheno_3)
  print(snake_max_pheno_3)
  print(min_difference_3)
  print(max_difference_3)
  if (newt_max_pheno_3 > snake_max_pheno_3){
    true_max_3 = newt_max_pheno_3 }
  if ( snake_max_pheno_3 > newt_max_pheno_3){
    true_max_3 = snake_max_pheno_3 }

  if (newt_min_pheno_3 < snake_min_pheno_3){
    true_min_3 = newt_min_pheno_3 }
  if ( snake_max_pheno_3 < newt_max_pheno_3){
    true_min_3 = snake_min_pheno_3 }
```
some of these values are in quotes, why?

```{r pressure, echo=FALSE}

files <- list.files(path="~/Desktop/pheno_test_1000_2/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
file1 <- read.table(files[1], header = TRUE)
p <- ggplot(file1, aes(x=gen)) +
  xlim(0, 1000)+
  #ylim(0, true_max_3)+
  #scale_y_continuous(trans=log10_trans(), limits=c(0,true_max_3))+
  #scale_y_log10()+
  scale_y_log10(limits=c(0.001,true_max_3))+
  geom_line(aes(y = Newt_mean_Pheno), color = "darkred") + 
  geom_line(aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash")+
  ggtitle("Phenotype Measurements for Newts and Snakes") +
  xlab("Generation") + ylab("Average Phenotypes")+
  theme_bw()

  file <- read.table(current_file, header = TRUE)
  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA

 p <- p +
  geom_line(data=file, aes(y = as.numeric(Newt_mean_Pheno)), color = "darkred",na.rm=TRUE) + 
  geom_line(data=file, aes(y = as.numeric(Snake_mean_Pheno)), color="steelblue", linetype="twodash", na.rm=TRUE) 
  #Sys.sleep(2) na.rm=TRUE

}

p 
```

Some other things that might be goo to look at:

The difference between the average phenotypes

```{r pressure, echo=FALSE}

files <- list.files(path="~/Desktop/pheno_test_1000_2/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
file1 <- read.table(files[1], header = TRUE)
p <- ggplot(file1, aes(x=gen)) +
  xlim(0, 1000)+
  #ylim(min_difference, max_difference)+
  #scale_y_continuous(trans=log10_trans(), limits=c(min_difference, max_difference))+
  #scale_y_log10()+
  scale_y_log10(limits=c(min_difference_3, max_difference_3))+
  geom_line(aes(y = Snake_mean_Pheno - Newt_mean_Pheno), color = "mediumseagreen") + 
  ggtitle("Difference Between Phenotypes (Snakes-Newts)") +
  xlab("Generation") + ylab("Average Difference")+
  theme_bw()

  file <- read.table(current_file, header = TRUE)
  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA
  file <- file[complete.cases(file), ]
  file$mean_dif = as.numeric(file$Snake_mean_Pheno) - as.numeric(file$Newt_mean_Pheno)
  file$mean_dif[file$mean_dif == 0] <- 0.01
  file$pos <- TRUE
  file$pos[file$mean_dif < 0] <- FALSE

 p <- p + geom_line(data=file, aes(x=gen, y=abs(mean_dif), color = pos), na.rm=TRUE)
  #Sys.sleep(2) na.rm=TRUE
 # color = "mediumseagreen"

}

p 
```
